---
title       : Default credit card payments in Taiwan.
subtitle    : 
author      : Yves Ef
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## Introduction

This research employed a binary variable, default payment (Yes = 1, No = 0), as the response variable. This study reviewed the literature and used the following 23 variables as explanatory variables: 

* X1: Amount of the given credit (NT dollar): it includes both the individual consumer credit and his/her family (supplementary) credit.
* X2: Gender (1 = male; 2 = female).
* X3: Education (1 = graduate school; 2 = university; 3 = high school; 4 = others).
* X4: Marital status (1 = married; 2 = single; 3 = others).
* X5: Age (year).
* X6 - X23: Click here: http://archive.ics.uci.edu/ml/datasets/default+of+credit+card+clients

For this project we have choosed the logistic regression to predict default payment variable and only 5 variables as predictor: X1(LIM_BAL), X2(Gender), X3(Education), X4(Marital status) and X5(Age).

---

## Analysis

### 1. Reading data and processing
```{r libraries, include=FALSE, cache=FALSE}
suppressPackageStartupMessages(TRUE)
require(gdata)
require(e1071) 
require(caret)
```

```{r reading_processing, cache=TRUE}
filename <- 'CreditCard.xls'
  
  if(file.exists(filename)==FALSE){
    download.file('http://archive.ics.uci.edu/ml/machine-learning-databases/00350/default%20of%20credit%20card%20clients.xls',filename,mode = 'w', quiet = TRUE)
  }
    Cdata <- read.xls(filename,pattern = 'ID')
  okData <- data.frame(EDUCATION=factor(Cdata$EDUCATION),SEX=factor(Cdata$SEX),
                       MARRIAGE=factor(Cdata$MARRIAGE),AGE=Cdata$AGE,
                       LIMIT_BAL= Cdata$LIMIT_BAL,
                       default.payment.next.month=factor(Cdata$default.payment.next.month)
  )
```

---

### 2. Fit the prediction model
```{r fitting_validation, cache=FALSE, echo=FALSE}
  inTrain <- createDataPartition(okData$default.payment.next.month,p=0.75,list=FALSE)
  training <- okData[inTrain,]
  testing  <- okData[-inTrain,]
  modelFit <- train(default.payment.next.month~., data=training, method='glm')
  summary(modelFit)$coefficients
```

---
### 3.  Test and validation
```{r validation, cache=FALSE, echo=FALSE,tidy=TRUE}
pred.test <- predict(modelFit, newdata=testing)
  confusionMatrix(pred.test,testing$default.payment.next.month)
```


